%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for CV/Resume
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)


%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt, a4paper]{awesome-cv}

% Configure page margins with geometry
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
% \colorlet{awesome}{awesome-skyblue}
% Uncomment if you would like to specify your own color
\definecolor{awesome}{HTML}{5E81AC}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{2E3440}
% \definecolor{text}{HTML}{3B4252}
% \definecolor{graytext}{HTML}{4C566A}
% \definecolor{lighttext}{HTML}{D8DEE9}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}

%===============================================================================
%   PERSONAL INFORMATION
%===============================================================================

% Available options: circle|rectangle,edge/noedge,left/right
% \photo[rectangle,edge,right]{./examples/profile}
% \photo[circle,edge,right]{profile.png}
\name{Lento}{Manickathan}
\position{Postdoctoral Researcher{\enskip\cdotp\enskip}Aerospace Engineer}
\address{Geissbergstrasse 22, 8200 Schaffhausen, Switzerland}

\mobile{(+41) 78 917 8121}
\email{lento.manickathan@gmail.com}
\homepage{https://manickathan.ch}
\github{lento234}
% \linkedin{lento-manickathan}
% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \twitter{@twit}
% \skype{skype-id}
% \reddit{reddit-id}
% \medium{madium-id}
% \googlescholar{b8RcAAAAJ}{Google Scholar}
%% \firstname and \lastname will be used
% \googlescholar{googlescholar-id}{}
\extrainfo{Swiss C permit}

% \quote{``Be the change that you want to see in the world."}


%-------------------------------------------------------------------------------
\begin{document}

% Print the header with above personal informations
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader[C]

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
\makecvfooter
  {\today}
  {Lento Manickathan}
  %   {Lento Manickathan~~~·~~~CV}
  {\thepage}


%===========================================================================
%   SUMMARY
%===========================================================================

\cvsection{Summary}

\begin{cvparagraph}

Aerospace Engineer and PhD in mechanical engineering with expertise in high-performance computing and machine learning. Keen at developing skills in computer vision techniques. A brief summary of expertise:

\begin{cventries}
    \begin{cvitems}
        \item {CFD simulation with OpenFOAM}
        \item {PIV experimental skills}
        \item {Machine learning with PyTorch}
        \item {Cloud computing, GPU computing}
        \item {Programming in Python}
        \item {Administration of HPC system}
    \end{cvitems}
\end{cventries}

\end{cvparagraph}

%===========================================================================
%   ACADEMIC & PROFESSIONAL EXPERIENCE
%===========================================================================

\cvsection{Academic \& Professional Experience}

\begin{cventries}

  \cventry
    {Postdoctoral researcher} % Job title
    {Empa} % Organization
    {Z\"urich, Switzerland} % Location
    {Jun. 2019 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Application of machine learning in quantitative flow visualization.}
        \item {Supervised optical flow algorithms for PIV.}
        \item {Convolutional Neural Networks (CNN) in PyTorch.}
        \item {Additional responsibilities: Lab HPC support, Fluid Tunnel support, Deputy Laser safety officer (LSO), and Deputy data management.}
      \end{cvitems}
    }

  \cventry
    {Scientific Assistant} % Job title
    {ETH Zurich} % Organization
    {Z\"urich, Switzerland} % Location
    {May 2015 - May 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Numerical and experimental research at Empa.}
        \item {Neutron radiography at Paul Scherrer Institute (PSI).}
        \item {Teaching assistant for Application of CFD in buildings.}
        \item {Supervision of master thesis project: \textit{Praharsh Pai Raikar}.}
      \end{cvitems}
    }

\end{cventries}


%===========================================================================
%   EDUCATION
%===========================================================================

\cvsection{Education}

\begin{cventries}

  \cventry
    {Ph.D. in Mechanical Engineering} % Degree
    {ETH Zurich} % Institution
    {Z\"urich, Switzerland} % Location
    {May 2015 - Jun. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {\textbf{Thesis}: Impact of Vegetation on Urban Microclimate.}
        \item {\textbf{Advisor}: Prof. Dr. Jan Carmeliet}
        \item {Development of a coupled soil-vegetation-air-radiation model in C++ within the OpenFOAM library.}
        \item {Wind tunnel study of flow past model and natural plants using PIV.}
        \item {X-ray tomography of small natural plants and high-performance big data analysis in python (HDF5, scikit-image, Dask, Numba).}
      \end{cvitems}
    }

  \cventry
    {M.Sc. in Aerospace Engineering} % Degree
    {TU Delft (Delft University of Technology)} % Institution
    {Delft, The Netherlands} % Location
    {Sep. 2011 - Dec. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {\textbf{Major}: Aerodynamics and Wind Engineering}
        \item {\textbf{Thesis}: Hybrid Eulerian-Lagrangian Vortex Particle Method: Developing a fast and accurate numerical method for the application of Vertical-Axis Wind Turbine (VAWT).}
        \item {\textbf{Advisor}: Dr. ir. Carlos Sim\~ao Ferreira}
        \item {Development of a high-performance numerical method in python with Cython and GPU (CUDA) acceleration.}
      \end{cvitems}
    }

  \cventry
    {B.Sc in Aerospace Engineering} % Degree
    {TU Delft (Delft University of Technology)} % Institution
    {Delft, The Netherlands} % Location
    {Sep. 2008 - Aug. 2011} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {\textbf{Minor}: Wind Energy and Sustainability}
        \item {\textbf{Thesis}: Designing a multi-purpose autonomous aerial monitoring aircraft.}
        \item {Design a UAV that can cope with severe weather conditions, while performing a variety of sensing and monitoring tasks.}
      \end{cvitems}
    }

\end{cventries}


%===========================================================================
%   EXTRACURRICULAR ACTIVITIES
%===========================================================================

\cvsection{Extracurricular Activities}

\begin{cventries}

  \cventry
    {Editor} % Degree
    {Leonardo Times Magazine} % Institution
    {Delft, The Netherlands} % Location
    {Sep. 2011 - Aug. 2012} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Journal of the Society for Aerospace Engineering students, the VSV \textit{Leonardo da Vinci} at the Delft University of Technology.}
        \item {In charge of current affairs section.}
      \end{cvitems}
    }

  \cventry
    {Powertrain Engineer} % Degree
    {TU Delft Formula Student} % Institution
    {Delft, The Netherlands} % Location
    {Sep. 2009 - Jul. 2010} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {In charge of designing the powertrain intake system.}
        \item {Design and production of the carbon-fiber intake system.}
        \item {\textit{2010 Formula Student Germany Champion.}}
      \end{cvitems}
    }

\end{cventries}


%===========================================================================
%   COMPUTER SKILLS
%===========================================================================

\cvsection{Skills}

\begin{cvskills}
  \cvskill
    {CAD}
    {Blender, CATIA}
  \cvskill
    {CFD}
    {FEniCS, Fluent, OpenFOAM}
  \cvskill
    {DevOps}
    {Ansible, AWS (EC2), TravisCI, Docker, Git, Grafana, Kubernetes, Nginx, Vagrant}
  \cvskill
    {Database}
    {InfluxDB, MariaDB}
  \cvskill
    {Embedded Platform}
    {Arduino, NVIDIA Jetson Nano, Raspberry Pi}
  \cvskill
    {Markup / Typesetting}
    {Jinja, LaTeX, Markdown, Vim}
  \cvskill
    {ML Libraries}
    {PyTorch, Scikit-learn}
  \cvskill
    {OS}
    {Linux (RedHat, Debian), Mac, Windows}
  \cvskill
    {Programming}
    {C++, MATLAB, Python, R, shell}
  \cvskill
    {Python Libraries}
    {Cupy, Cython, Dask, H5py, Matplotlib, MPI4py, Numba, NumPy, Pandas, SciPy, Scikit-image}
  \cvskill
    {Web development} % Category
    {CSS, Hugo, HTML5}
\end{cvskills}

\cvsection{Languages}

\begin{cvskills}
    \cvskill
    {}
    {\textbf{English} (Fluent), \textbf{German} (Conversational), \textbf{Malayalam} (Fluent), \textbf{Dutch} (Basic)}
\end{cvskills}

%===========================================================================
%   HONORS & AWARDS
%===========================================================================

\cvsection{Honors \& Awards}

\begin{cvhonors}

  \cvhonor
    {Outstanding Oral Presentation} % Award
    {13th Symposium on Urban Environment} % Event
    {Seattle, USA} % Location
    {2017} % Date(s)
  \cvhonor
    {Young Best Researcher} % Award
    {4th International Conference on Countermeasures to Urban Heat Island} % Event
    {Singapore} % Location
    {2016} % Date(s)
\end{cvhonors}

%===========================================================================
%   PUBLICATIONS
%===========================================================================

\cvsection{Publications}

\begin{cventries}

  \pubentry
  {Journals} % Title
  {
    \begin{cvitems}
      \item {\textbf{Manickathan, L.}, Mucignat, C., Lunati, I.: Random displacement training for fluid flow motion estimation. 2022. (\textit{in preparation})}
      \item {\textbf{Manickathan, L.}, Defraeye, T., Carl, S., Richter, H., Allegrini, J., Derome, D., \& Carmeliet, J. (2022). A study on diurnal microclimate hysteresis and plant morphology of a Buxus sempervirens using PIV, infrared thermography, and X-ray imaging. \textit{Agricultural and Forest Meteorology} 313, 108722.}
      \item {\textbf{Manickathan, L.}, Defraeye, T., Allegrini, J., Derome, D., \& Carmeliet, J. (2018). Parametric study of the influence of environmental factors and tree properties on the transpirative cooling effect of trees. \textit{Agricultural and Forest Meteorology} 248, 259-274}
      \item {\textbf{Manickathan, L.}, Defraeye, T., Allegrini, J., Derome, D., \& Carmeliet, J. (2018). Comparative study of flow field and drag coefficient of model and small natural trees in a wind tunnel. \textit{Urban Forestry \& Urban Greening}, 35(December 2017), 230–239.}
    \end{cvitems}
  }
  \pubentry
  {Preprints}
  {
    \begin{cvitems}
      \item {Palha, A., \textbf{Manickathan, L.}, Ferreira, C. S., \& van Bussel, G. (2015). A hybrid Eulerian-Lagrangian flow solver.}
    \end{cvitems}
  }
  \pubentry
  {Conferences}
  {
    \begin{cvitems}
      \item {\textbf{Manickathan, L.}, Kubilay, A., Defraeye, T., Allegrini, J., Derome, D., \& Carmeliet, J.: Integrated CFD vegetation model with soil-plant-air water dynamics for studying the cooling potential of vegetation in an urban street canyon. \textit{10th International Conference on Urban Climate/14th Symposium on the Urban Environment}, New York, NY, USA, 6 - 10 August 2018.}
      \item {\textbf{Manickathan, L.}, Defraeye, T., Allegrini, J., Derome D., \& Carmeliet, J.: Conjugate Vegetation Model for Evaluating Evapotranspirative Cooling in Urban Environment. \textit{97th AMS Annual Meeting}, Seattle, WA, USA, 2017.}
      \item {\textbf{Manickathan, L.}, Defraeye, T., Allegrini, J., Derome, D., \& Carmeliet, J.: Aerodynamic characterization of model vegetation by wind tunnel experiments. \textit{4th International Conference on Countermeasures to Urban Heat Island}, Singapore, 2016.}
    \end{cvitems}
  }

\end{cventries}


\end{document}
